We study publisher-side privacy preprocessing for video datasets in which SAM2-based video object tracking must be reliably degraded while preserving perceptual quality after H.264/HEVC compression.
We propose \emph{boundary ring suppression} (BRS): a lightweight preprocessing step that replaces the narrow boundary region of annotated objects with a locally inpainted background, blending at strength~$\alpha$ over a ring of width~$r$.
Codec compression amplifies boundary-level feature destruction, making this class of method effective even under strict quality constraints.

The core scientific contribution is a proxy-validated \emph{soft surrogate-constrained} parameter selection procedure, \textbf{AdvOpt}, that discovers the codec-robust optimal operating point $(r^*, \alpha^*) \approx (24\text{ px},\, 0.93)$.
AdvOpt minimises a pre-codec boundary gradient proxy under a soft SSIM surrogate constraint (MSE-based), requiring only the first annotated frame.
AdvOpt is an offline calibration tool: once the operating point is discovered, it can be applied globally without per-video re-optimisation.
We validate the proxy via within-video Pearson correlation ($r=+0.811$) and an oracle-gap experiment in which the proxy-selected $\alpha$ matches the oracle optimal $\alpha$ on $98\%$ of DAVIS videos.

Experiments on DAVIS (90 videos) show that AdvOpt achieves a mean post-codec tracking degradation of $+57.7\,\mathrm{pp}$ ($\Delta\mathrm{JF}_{\mathrm{codec}}$) versus $+24.7\,\mathrm{pp}$ for a fixed baseline ($\alpha{=}0.80$), with win-rate $91.7\%$ and $t=7.68$.
Crucially, a global-fixed setting $(r=24, \alpha=0.93)$ achieves equivalent performance ($+0.3\,\mathrm{pp}$ difference, $t=0.31$, $n=27$), confirming that AdvOpt discovers a near-universal codec-robust operating point rather than exploiting video-specific idiosyncrasies.
A direct fair comparison on YT-VOS ($n=50$, H.264 CRF=23) confirms that AdvOpt converges to $\alpha{>}0.92$ for $88\%$ of videos ($94\%$ of paired gains within $\pm 5\,\mathrm{pp}$), with the small mean difference ($-0.82\,\mathrm{pp}$, $t{=}{-}2.08$) driven entirely by $12\%$ of videos where the MSE surrogate over-penalises (surrogate brittleness).
The recommended deployment strategy is therefore \emph{global-fixed BRS} at the AdvOpt-discovered point $(r{=}24,\alpha{=}0.93)$.
Generalization holds across codecs (HEVC: $+28.5\,\mathrm{pp}$), datasets (YT-VOS full sweep $n{=}497$: $+9.2\,\mathrm{pp}$, $91.9\%$ wins), and partially across trackers (XMem: $17.6\,\mathrm{pp}$).
We report the privacy-utility tradeoff honestly: SSIM $\geq 0.90$ for $94\%$ of videos; downstream object-detection recall drops from $77.5\%$ (fixed baseline) to $55.2\%$ (AdvOpt).
