\section{Baselines, Generalization, and Utility}
\label{sec:baselines}

\subsection{Uniform BRS: Full DAVIS Sweep}

We first establish the strength of uniform BRS itself on the full DAVIS evaluation set.

\begin{table}[t]
\centering
\small
\caption{Uniform BRS on DAVIS ($n{=}74$ paired videos, H.264 CRF=23, point prompt). AdvOpt is an offline calibration tool; global-fixed applies its discovered operating point.}
\label{tab:davis_full}
\begin{tabular}{lcccc}
\toprule
\textbf{Method} & \textbf{$\Delta$JF (pp)} & \textbf{SSIM} & \textbf{Win-rate} & \textbf{$t$-stat} \\
\midrule
Fixed $\alpha{=}0.80$ (idea1) & 22.0 & 0.956 & baseline & --- \\
AdvOpt ($\alpha{\approx}0.93$) & \textbf{53.0} & 0.943 & 93.2\% & 10.87 \\
Global-fixed ($r{=}24, \alpha{=}0.93$) & $\approx$53.0 & 0.943 & equiv. & $t{=}0.31$ \\
\bottomrule
\end{tabular}
\end{table}

AdvOpt and global-fixed are statistically equivalent ($+0.3\,\mathrm{pp}$, $t{=}0.31$, $n{=}27$).
AdvOpt serves as an offline calibration tool that discovered the operating point; global-fixed application is sufficient for deployment.

\subsection{Matched-Quality Baselines}

A critical question is whether BRS outperforms simpler publisher-side transforms at matched visual quality.
We compare against four alternatives, each tuned to match the BRS operating-point SSIM (${\approx}0.94$):

\begin{itemize}
  \item \textbf{Boundary blur:} Gaussian blur restricted to the boundary ring (same spatial support as BRS).
  \item \textbf{Global blur:} Gaussian blur applied to the entire frame.
  \item \textbf{Pixelation:} Downsample-then-upsample the boundary region at a block size tuned to match SSIM.
  \item \textbf{Inpainting:} OpenCV Telea inpainting of the boundary ring.
\end{itemize}

% TODO: fill in after running eval_baselines.py
% \begin{table}[t]
% \centering
% \small
% \caption{Matched-quality baseline comparison (DAVIS $n{=}30$, H.264 CRF=23, SSIM matched to ${\approx}0.94$).}
% \label{tab:baselines}
% \begin{tabular}{lccc}
% \toprule
% \textbf{Method} & \textbf{$\Delta$JF (pp)} & \textbf{SSIM} & \textbf{Win-rate vs.\ BRS} \\
% \midrule
% BRS ($r{=}24, \alpha{=}0.93$) & 53.0 & 0.943 & --- \\
% Boundary blur & ?.? & 0.94$\pm$ & ?/? \\
% Global blur & ?.? & 0.94$\pm$ & ?/? \\
% Pixelation & ?.? & 0.94$\pm$ & ?/? \\
% Inpainting & ?.? & 0.94$\pm$ & ?/? \\
% \bottomrule
% \end{tabular}
% \end{table}

Preliminary results from the pareto sweep ($n{=}28$) show boundary blur achieves $9.1\,\mathrm{pp}$ at comparable SSIM, versus $11.3\,\mathrm{pp}$ for idea1---suggesting BRS's flat-mean proxy is meaningfully more effective than blur at creating codec-amplified boundary destruction.

\subsection{Generalization}

\begin{table}[t]
\centering
\small
\caption{Generalization of uniform BRS across codecs, datasets, and trackers.}
\label{tab:generalization}
\begin{tabular}{llccc}
\toprule
\textbf{Axis} & \textbf{Setting} & \textbf{$n$} & \textbf{$\Delta$JF (pp)} & \textbf{Win-rate} \\
\midrule
Codec    & HEVC CRF=23  & 17  & 28.5 & 88.2\% \\
Dataset  & YT-VOS full  & 497 & 9.2  & 91.9\% \\
Dataset  & YT-VOS fair  & 50  & $-0.82$ (vs.\ fixed) & 94\% within $\pm 5$pp \\
Tracker  & XMem         & 19  & 17.6 & --- \\
\bottomrule
\end{tabular}
\end{table}

BRS generalises across codecs (HEVC: $+28.5\,\mathrm{pp}$), datasets (YT-VOS $n{=}497$: $+9.2\,\mathrm{pp}$), and partially across trackers (XMem: $17.6\,\mathrm{pp}$, attenuated versus SAM2 due to XMem's lower reliance on boundary features).
The YT-VOS fair comparison confirms that per-video AdvOpt and global-fixed are near-equivalent ($94\%$ of gains within $\pm 5\,\mathrm{pp}$).

\subsection{Privacy-Quality-Utility Tradeoff}

\paragraph{Quality.}
At the operating point, $\mathrm{SSIM}{=}0.943$ and $\mathrm{LPIPS}{=}0.096$ ($n{=}20$ DAVIS).
We do not claim visual imperceptibility; the appropriate characterisation is \emph{quality-constrained privacy protection} with bounded distortion.

\paragraph{Frontier.}
A parameter sweep ($r \in \{6,8,10,12,14,16,20,24\}$, $n{=}8$ per point) reveals a monotone privacy-quality frontier: under $\mathrm{SSIM}{\geq}0.95$, uniform BRS is capped at ${\sim}20\,\mathrm{pp}$.
This ceiling motivates the anisotropic direction: to achieve stronger privacy at high fidelity, the budget must be \emph{redirected}, not increased.

\paragraph{Downstream utility.}
YOLO detection recall drops from $77.5\%$ (baseline) to $55.2\%$ (BRS at $\alpha{=}0.93$), a deliberate privacy cost.
The method is designed for publishers prioritising tracking prevention over downstream annotation utility.
