\section{Conclusion}
\label{sec:conclusion}

We presented \textbf{AdvOpt}, a proxy-validated soft surrogate-constrained parameter selection procedure for boundary ring suppression (BRS), a lightweight privacy preprocessing method that degrades SAM2-based video object tracking after H.264/HEVC codec compression while preserving perceptual quality.
AdvOpt is best understood as an \emph{offline calibration tool}: it discovers the codec-robust operating point once, after which the discovered parameters can be applied globally without per-video re-optimisation.

The central finding is a near-universal codec-robust operating point $(r^*\approx 24\,\mathrm{px},\, \alpha^*\approx 0.93)$ that can be discovered per-video via AdvOpt or applied globally with equivalent effect.
On DAVIS ($n=27$ paired), a global-fixed setting with these parameters achieves the same performance as per-video optimization ($+0.3\,\mathrm{pp}$, $t=0.31$), confirming that AdvOpt's role is operating-point \emph{discovery} rather than video-specific tuning on homogeneous content.
On heterogeneous content (YT-VOS), $88\%$ of videos converge to the same operating point; the remaining $12\%$ require lower $\alpha$ to maintain the SSIM quality constraint, demonstrating the proxy's role in constraint-aware selection.

The proxy (within-video $r=+0.811$, oracle-gap $98\%$) provides a principled and computationally cheap validation that the selected parameters are near-optimal without requiring codec-in-the-loop optimization.
Generalization across codecs (HEVC) and trackers (XMem, $17.6\,\mathrm{pp}$) suggests boundary-level feature destruction is a codec-robust mechanism beyond SAM2.

We acknowledge the privacy-utility tradeoff explicitly: the method maintains $\mathrm{SSIM}\geq 0.90$ on average but with a $6\%$ soft-constraint violation rate, and downstream object-detection recall drops by $\sim 22\,\mathrm{pp}$ relative to the unprocessed baseline.
This method is best suited for dataset publishers who need strong, codec-robust privacy guarantees and can tolerate a deliberate utility reduction.

Future work includes: end-to-end differentiable codec-in-loop optimization, extension to non-boundary-dependent trackers, and adaptive utility controls that jointly optimize privacy and downstream task preservation.
