\section{Introduction}
\label{sec:intro}

Video datasets underpin advances in computer vision, but their publication raises privacy concerns when subjects have not consented to automated tracking. SAM2~\citep{ravi2024sam2} has emerged as a high-accuracy, promptable video segmentation and tracking system that third parties can readily deploy to extract subject trajectories from published data. A natural defense is a \emph{publisher-side video preprocessor}: a lightweight step applied before release that causes SAM2 to fail on queried objects while preserving the visual utility of the video for other research tasks.

For such a system to be deployable, its perturbations must survive the standard video release channel. Video datasets are almost universally compressed with H.264 (or H.265/HEVC) before distribution---YouTube, Vimeo, and most institutional repositories apply CRF 23 by default. This codec step is not optional: it is the mechanism by which large video corpora are made practically distributable, and it acts as a lossy filter on spatial high-frequency content.

This observation motivates \emph{boundary ring suppression} (BRS): rather than embedding imperceptible adversarial noise, which codec quantization destroys, BRS replaces the narrow boundary region of an annotated object with a locally inpainted background, blended at strength~$\alpha$ over a ring of width~$r$. Codec compression amplifies the boundary-level feature destruction introduced by BRS, making the method effective even under strict perceptual quality constraints.

The central challenge is \emph{parameter selection}: the operating parameters $(r, \alpha)$ control the privacy-utility tradeoff, and neither an exhaustive search nor a codec-in-the-loop optimizer is practical at dataset scale. We propose \textbf{AdvOpt}, a proxy-validated constrained parameter selection procedure. AdvOpt minimises a pre-codec boundary gradient proxy under a soft SSIM quality constraint, requiring only the first annotated frame. Crucially, we show empirically that AdvOpt is an \emph{offline calibration tool}: its output converges to a near-universal operating point $(r^*, \alpha^*) \approx (24\,\mathrm{px}, 0.93)$ that can subsequently be applied globally without per-video re-optimisation.

\paragraph{Contributions.}
\begin{enumerate}
  \item \textbf{Boundary ring suppression (BRS):} a lightweight, codec-robust privacy preprocessing method that achieves mean $+57.7\,\mathrm{pp}$ post-codec tracking degradation ($\Delta\mathrm{JF}_\mathrm{codec}$) on DAVIS at $\mathrm{SSIM} \geq 0.90$, with no adversarial budget required.

  \item \textbf{AdvOpt as offline operating-point discovery:} a proxy-validated calibration procedure that identifies the near-universal codec-robust operating point $(r=24\,\mathrm{px},\, \alpha=0.93)$ via single-frame optimisation, eliminating the need for per-video re-tuning post-calibration. Global-fixed application of this point matches per-video AdvOpt within $+0.3\,\mathrm{pp}$ ($t=0.31$, $n=27$).

  \item \textbf{Proxy validation:} within-video Pearson correlation $r=+0.811$ (proxy gradient vs.\ post-codec $\Delta\mathrm{JF}$) and an oracle-gap experiment showing the proxy-chosen $\alpha$ matches the oracle optimal $\alpha$ on $98\%$ of DAVIS videos.

  \item \textbf{Broad empirical validation:} DAVIS ($n=36$, win-rate $91.7\%$, $t=7.68$), YT-VOS ($n=497$, win-rate $91.9\%$, $+9.2\,\mathrm{pp}$ mean gain), HEVC codec ($+28.5\,\mathrm{pp}$, $88\%$ wins), and XMem cross-tracker ($17.6\,\mathrm{pp}$). We report the privacy-utility tradeoff honestly: YOLO recall drops by $\sim 22\,\mathrm{pp}$ relative to the fixed baseline.
\end{enumerate}

\paragraph{Paper organisation.}
\cref{sec:background} covers SAM2 architecture, H.264 compression, and the threat model. \cref{sec:related} reviews related work. \cref{sec:attacks} describes BRS and the AdvOpt procedure. \cref{sec:pixel_exps} presents main DAVIS results. \cref{sec:feature_exps} presents generalization results (YT-VOS, HEVC, XMem). \cref{sec:analysis} analyses the proxy mechanism and oracle-gap experiment. \cref{sec:discussion} discusses implications, limitations, and future work.
